Language learning in context via recursive pragmatic reasoning

### 2013-05-31 praglearn.tex
conclusion

\title{Language learning via recursive pragmatic reasoning}
% \title{Learning words via recursive pragmatic reasoning about other agents}
% : The blessing of social anxiety - not a huge fan of colon titles

@@

Our work identifies two biases in communicators' behavior: a tendency for pragmatic speakers
and listeners to accentuate useful, sparse patterns in their
communicative systems (\S\ref{sec:emergence}), and for short,
high-frequency (``low cost'') expressions to
be assigned to common objects (\S\ref{sec:horn-emergence}).
Remarkably, while both of these biases are locally sub-optimal for individual agents,
they both systematically drive the overall communicative system
towards greater global efficiency. In the long term, these processes
should leave their mark on the structure of the language itself, which
may contribute to explaining how languages become 
optimized for effective communication \cite{zipf1936,piantadosi2011}.

>>>>

\title{Language learning in context via recursive pragmatic reasoning}
% \title{Learning words via recursive pragmatic reasoning about other agents}
% : The blessing of social anxiety - not a huge fan of colon titles

@@

Our work identifies two biases in communicators' behavior: a tendency for pragmatic speakers
and listeners to accentuate useful, sparse patterns in their
communicative systems (\S\ref{sec:emergence}), and for short,
high-frequency (``low cost'') expressions to
be assigned to common objects (\S\ref{sec:horn-emergence}).
Both of these biases systematically drive the overall communicative system
towards greater global efficiency. In the long term, these processes
should leave their mark on the structure of the language itself, which
may contribute to explaining how languages become 
optimized for effective communication \cite{zipf1936,piantadosi2011}.

More generally, considering the interaction between pragmatics and learning may be a critical part of understanding human language. Our work here takes a first step towards unifying disparate strands of research that have treated language acquisition and language use as distinct.
